\documentclass[12pt, tweaklist, line]{res}

% compile with: pdflatex --file-line-error --synctex=1 sam.tex

% Hyperlinks
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}
% Change global itemize settings
\let\tempone\itemize
\let\temptwo\enditemize
\renewenvironment{itemize}{\tempone\vspace{-.15in}\setlength{\topsep}{0pt}\setlength{\itemsep}{3pt}\vspace{-.15in}}{\temptwo}

% Macros
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}
\newcommand{\ts}{\textsuperscript}

% Use only a bit more of the page than the default
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\voffset}{-0.50in}
\addtolength{\textwidth}{0.90in}
\addtolength{\textheight}{1.70in}

\begin{document}

% Header
\begin{center}
    \hspace{-1.5cm}\Huge\textbf{Samantha Hughes}
\end{center}
\vspace{-.2in}
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
    \hspace{-1.5cm} UK +44 7540 531774 & \href{mailto:shughes.uk@gmail.com}{shughes.uk@gmail.com} \\
    \hspace{-1.5cm} US +1 (512) 909-9300 & ~ \\
\end{tabular*}
\hrulefill

\begin{resume}

% Open Source
\section{Open Source}
\begin{itemize}
\vspace{.55in} % why do I need to manually put vertical space here?
\item \href{http://www.evecharactersearch.com/}{Eve Character Search}: Enables marketplace search and interaction for Eve Online character sales. Built on web scraping, aggregation, and filtering technologies. Serves around 3,000 unique visitors per month.
\item \href{https://github.com/shughes-uk/python-twitchchat}{python-twitchchat}: Python library that uses asyncore to connect to Twitch Messaging Interface and provide event driven subscriptions.
\item \href{https://github.com/shughes-uk/twitch_button}{twitch\_button}: Integrates \href{https://obsproject.com/}{Open Broadcaster Software} with a USB button, an \href{http://blinkinlabs.com/blinkytape/}{RGB striplight}, \href{http://www2.meethue.com/}{Philips Hue}, and the \href{http://twitch.com}{Twitch.com} API. Provides real-time feedback and control during online streaming.
\item \href{https://github.com/shughes-uk/twitchchat_display}{twitchchat\_display}: Runs on a RaspberryPi using pyGame to display twitch.com chat on a large screen for easy monitoring during streams.
\item \href{https://github.com/shughes-uk/ArtPad}{ArtPad}: WoW add-on for a multi-user cooperative online drawing paint program.
\item \href{https://github.com/shughes-uk/streamingopt}{streamingopt}: Tool for optimizing H.264 encoding for live streaming.
\item \href{https://github.com/shughes-uk/litequeue}{litequeue}: Stripped down and highly optimized version of popular WoW add-on oQueue.
\item \href{https://github.com/shughes-uk/facesofReddit}{facesofReddit}: Monitored reddit for images containing faces using face.com API. Face.com was bought by Facebook and is now defunct.
\end{itemize}

% Experience
\section{Experience}
\begin{format}
  \employer{l}\location{r}\\
  \title{l}\dates{r}\\
  \body\\
\end{format}

% WebBrick
\employer{\textbf{WebBrick Systems}}
\title{Software Engineer}
\location{Theale, UK}
\dates{June 2009 -- January 2011}
\begin{position}
\begin{itemize}
\item Integrated high end media center equipment with home automation equipment.
\item Learned and then leveraged Python to interface with RS232 and telnet devices.
\end{itemize}
\end{position}

%  Lo-Q
\employer{\textbf{Accesso} (\textbf{formerly Lo-Q})}
\title{Junior Software Developer}
\location{Henley, UK}
\dates{June 2008 -- October 2008}
\begin{position}
\begin{itemize}
\item Created WiFi repeater device administration software to manage dozens of remote devices.
\item Was kept on after completion of Reading University SEED placement program.
\item Learned and became proficient in .NET and C\# while on the job.
\end{itemize}
\end{position}

% Education
\section{Education}
\begin{format}
  \employer{l}\location{r}\\
  \title{l}\dates{r}\\
  \body\\
\end{format}

% TAMU
\employer{\textbf{Reading University}}
\title{3\ts{rd} year of A.I. \& Cybernetics B.S. }
\location{Reading, UK}
\dates{2006 -- 2010}
\begin{position}
\begin{itemize}
\item Wrote a polyalphabetic cipher cracking program in \Cplusplus~using a genetic algorithm.
\item Created a neural network in \Cplusplus~and applied it to prediction of gross domestic product.
\item Built and programmed a mobile robot which could avoid obstacles and solve a maze.
% \item Created a simple autonomous agent and knowledge database in Prolog.
% \item Worked in C# to implement various algorithms including a infix to post/prefix expression converter.
% \item Created a website based on specifications from professional website Development Company Heathwallace using asp.NET.
\end{itemize}
\end{position}

\pagebreak

% Skills
\section{Skills}

~\\ % why is this necessary to get skills section to correctly format?

\begin{itemize}
\item \textbf{Languages:} Python, C\#, Lua, C, \Cplusplus, Java, JavaScript
\item \textbf{Tools:} git, Atom, Visual Studio
\item \textbf{Libraries:} Django, .NET, BeautifulSoup, pySerial, pyYAML, pyQT
\item \textbf{Markup:} YAML, XML, HTML/CSS, Markdown
\item \textbf{Operating Systems:} Windows, Linux (Ubuntu and Debian based), OS X
% \item \textbf{Databases:} SQLite
\end{itemize}

\end{resume}
\end{document}
